---
title: "Introduction to the vaers package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the vaers package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vaers)
```

This gives a brief introduction into the vaers package.

## Datasets

This package includes the datasets: vaers_2010, vaers_2011, ..., vaers_2020.

These datasets stem from the "Vaccine Adverse Event Reporting System (VAERS)" and contain information about different vaccinations and the corresponding adverse events.

## Functions

This package also contains to functions which makes the preprocessing of the vaers data easier:

### create_dummy()

This functions searches for given keywords in the columns symptom1 - symptom5 (using regEx) and creates a dummy variable for a specific symptom.

```{r}
newdata = create_dummy(data = vaers_2020, name = "headache", symptoms = c("Headache"))
head(newdata)
```


### create_dataset()

This function takes a vaers dataset or a dataset from the output of the create_dummy() function filters for a specific vaccine name and reorders the columns of the dataframe.

```{r}
newdata = create_dataset(data = vaers_2020, vaxname = "COVID19 (COVID19 (JANSSEN))")
head(newdata)
```


### show_vaccines()

In order to use the create_dataset() function it might be helpful to have a list of the vaccine names. This function provides this list, just insert the dataset of interest.

```{r}
show_vaccines(data = vaers_2020)
```


